### 2012-11-15 doc/progress_plan/report.tex
Finished talking about pdf extraction stuff

@@

Initially, the PDF conversion subroutine had a very high error rate due to high
variation in the formatting of scientific papers. It was suggested that PDFX (\url{http://pdfx.cs.man.ac.uk/})
a free service hosted by the University of Manchester could be used instead of
PDFMiner for the initial PDF data extraction. The main advantage of PDFX over
the PDFMiner library is that is a trained machine learning system that has been
trained using a large full-text selection of articles; PDFX's classifier is
more suited to paper conversion than PDFMiner's more general heuristic
approach.

PDFX's main advantage is that it uses a machine learning system to
guess PDF document structures more accurately than through the use of simple
Heuristics. With an adapted backend that sends PDFs for analysis using PDFX and
then splits the results using NLTK, the conversion script now has a much higher
success rate and will be used as a preprocessor for adding PDF  documents to
Partridge.

>>>>

\subsubsection{ Sourcing Scientific Papers}
For Partridge to be a success, it is important to include a large variety of
different scientific papers in its corpus. Therefore, several sources of
scientific papers were explored and considered.

@@

Initially, the PDF conversion subroutine had a very high error rate due to the
variation in the formatting of scientific papers. It was suggested that PDFX
(\url{http://pdfx.cs.man.ac.uk/}) a free service hosted by the University of
Manchester could be used instead of PDFMiner for the initial PDF data
extraction. The main advantage of PDFX over the PDFMiner library is that is a
trained machine learning system that has been trained using a large full-text
selection of articles; PDFX's classifier is more suited to paper conversion
than PDFMiner's more general heuristic approach.

PDFX also provides output that already has some metadata, such as title,
author, and abstract, associated with it. PDFMiner did not provide any
metadata, and it was necessary for the script to guess which passage of text
was the abstract after the initial text extraction stage.

With the new PDF extraction method in place, the script ran without the need
to modify either of the whitespace sanitiser or sentence splitter routines. The
process was much more successful and able to produce SAPIENTA-compatible
documents from most of the PDF input files that were provided.
